\documentclass{acm_proc_article-sp}

\begin{document}

\setlength{\parindent}{15pt}

\title{Tag Recommendations in StackOverflow}
\subtitle{CS 224W Final Project: December 9, 2014}

\numberofauthors{3}
\author{
  \alignauthor
  Logan Short\\
    \affaddr{lshort@stanford.edu}
  \alignauthor
  Christopher Wong\\
    \affaddr{crwong@stanford.edu}
  \alignauthor
  David Zeng\\
    \affaddr{dzeng0@stanford.edu}
}

\date{9 December 2014}

\maketitle

\begin{abstract}
Abstract goes here.
\end{abstract}

\section{Introduction}
Introduction goes here.

\section{Prior Work}
Prior work goes here.

\section{Data...}
Data... goes here.

\section{Results...}
Results... goes here.

\section{Conclusions and Future Work}
Conclusions and Future Work goes here.

\begin{thebibliography}{1}
\bibitem{1} X. Xia, D. Lo, X. Wang, B. Zhou. Tag Recommendation in Software Information Sites. MSR, 2013.
\bibitem{2} J. McAuley, J. Leskovec. Discovering Social Circles In Ego Networks. ACM TKDD, 2014.
\bibitem{3} L. Backstrom, D. Huttenlocher, J. Kleinberg, X. Lan. Group Formation in Large Social Networks: Membership, Growth, and Evolution. KDD, 2006.
\bibitem{4} J. Leskovec, K. Lang, A. Dasgupta, M. Mahoney. Statistical Properties of Community Structure in Large Social and Information Networks. WWW, 2008.
\bibitem{5} S. Wang, D. Lo, B. Vasilescu, A. Serebrenik. EnTagRec: An Enhanced Tag Recommendation System for Software Information Sites. ICSME, 2014.
\bibitem{6} Stack Exchange Data Dump (September 26, 2014). Retrieved 2 November 2014. https://archive.org/details/stackexchange.
\end{thebibliography}

%\balancecolumns

\end{document}
